Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-11-27 article.qmd
Format Compartment code
Expand legend for simulation figure

Simulation of the `Oscillator` system from @fig-second-order,
which outputs a `pandas.DataFrame`.
:::

@@

class Model(Compartment):
    """2A -> B"""
    A: Species = initial(default=1)
    B: Species = initial(default=0)
    r = Reaction(reactants=[2 * A], products=[B], rate_law=1)
```

>>>>

Simulation of the `Oscillator` system from @fig-second-order.
The output is a `pandas.DataFrame` with a column for each variable
and the time as index.
It is inspected and plotted with the `pandas` methods.
:::

@@

class Model(Compartment):
    """2A -> B"""

    A: Species = initial(default=1)
    B: Species = initial(default=0)
    r = Reaction(reactants=[2 * A], products=[B], rate_law=1)
